 JavaScript
-----------

-> JS
   --
   > is the world's most popular programming language.
   > is the programming language of the Web.
   > that allows you to implement complex functionalities on web pages.


-> Why?
   ---
 . used in building very fast server side and full stack apps
 . build very interactive user interfaces with frameworks like React
 . used in web(react js, node js, experess js), mobile(react-native) and desktop(Electron js)

 ------------------------------------------------------
-> Some topics
   ---- ------
 - variables & data types
 - arrays
 - object literals
 - methods for strings, arrays, objects, etc 
 - loops -> for , while, for..of, forEach, map
 - conditionals (if, ternary & switch)
 - functions { normal & arrow}
 - OOP (prototypes & classes)
 - DOM selection
 - DOM manipulation
 - Events
 - Basic form validstion

 ----------------------
 . Async
 . Fetch API & Ajsx
 . vanilla js
 . Framework like React, Vue etc...
 ----------------------
-------------------------------------------------------

-> Syntax
   ------
   - JavaScript syntax is the set of rules.

-> Semicolons
   ----------
   > Symbol ' ; '
   > Add a semicolon at the end of each executable statement
   > a = 5;  // Example


-> JavaScript can "display" data in different ways :
    ---------- --- --------  ---- -- --------- ---- 

    > Writing into an HTML element, using innerHTML.
    > Writing into the HTML output using document.write().
    > Writing into an alert box, using window.alert().
    > Writing into the browser console, using console.log().

-> JavaScript statements are composed of :
   ---------- ---------- --- -------- --
   - Values, Operators, Expressions, Keywords, and Comments.

----------------------------------------------------------------
# Values
   ------
   - Fixed values are called Literals.
      * boolean * character * numeric * string

   - Variable values are called Variables.
      * var * let  * const

# Variables
    ---------
    > are used to store data values.

    > Types :-
      -----
      * var - is globaly scoped 
      * let - a block level scope
      * const - a block level scope 
---------------------------------------------------------------------------------
  * var
  - ---
    . function-scoped variables that can be hoisted.
    . a var variable is visible to the whole function in which it is declared.
    . can be declared without being initialized.

 
  * Let
  - ---
    . block-scoped variables that can be reassigned.
    . while a let variable is only visible within the block in which it is declared.
    . let variables can be updated but not re-declared.
    . can be declared without being initialized.

  * Const
  - ----
    . block-scoped variables that are constant and cannot be reassigned.
    . const variables can neither be updated nor re-declared.
    . const must be initialized during declaration.
-------------------------------------------------------------------------------------

# Operators
   ---------
   > uses arithmetic operators ( + - * / ) to compute values.

# Expressions
   -----------
   > is a combination of values, variables, and operators, which computes to a value.

# keywords 
   --------
  > are used to identify actions to be performed.

# Identifiers 
   ---------
  > are JavaScript names.
  > unique names are called identifiers.
  
   - A letter (A-Z or a-z)
   - A dollar sign ($)
   - $ Or an underscore (_)
   
# Case Sensitive
  ---- ---------
  > identifiers are case sensitive.
  > Lower case and Upper case.

# Camel Case
  ----- ----
  > joining multiple words into one variable name:-

  - Hyphens: (-)
  - Underscore: (_)
  - Upper Camel Case: (FirstLast)
  - Lower Camel Case: (firstLast) // best option

# Character Set
  --------  ---
  - Unicode covers (almost) all the characters, punctuations, and symbols in the world.

# Comments
   -------
    * Single line comments   // here comment
    * Multi line comments   /* here comment */

---------------------------------------------------------------








